Price of Anarchy for Mean Field Games

### 2018-07-20 PoA.tex
limit top of page 22 more clear

	Our next step is to show that $(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2,t_2) } $ tends towards $0$ when $\bar{b}_2 \to \infty$. We showed above that for all $t \in [0,T]$, $f(\bar{b}_2,t) \to c_3 >0$. Thus, for any $0<\epsilon <\frac{c_3}{2} $, there exists $\bar{b}_2^* := \bar{b}_2^*(\epsilon,t_2)>0$ so that for all $\bar{b}_2 \geq \bar{b}_2^*$ we have $\vert f(\bar{b}_2,t_2) - c_3 \vert < \epsilon$. Then $f(\bar{b}_2,t_2) - c_3 + 2\epsilon > \epsilon$ and 
	\begin{equation*}
	\begin{array}{rll}
		(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2,t_2) }  &=& e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} (f(\bar{b}_2,t_2) - c_3 + 2\epsilon) }\cdot e^{- \kappa  (c_3 - 2 \epsilon) (b_2 + \bar{b}_2)^{\frac{1}{2}} +  \ln (b_2 + \bar{b}_2) } \\
		& \leq & e^{- \kappa (b_2+\bar{b}_2^*)^{\frac{1}{2}} \cdot \epsilon} \cdot e^{- \kappa (c_3 - 2 \epsilon) (b_2 + \bar{b}_2)^{\frac{1}{2}} + \ln (b_2 + \bar{b}_2)} 
	\end{array}
	\end{equation*}
	(ToDo: problem here. What is the limit of $e^{- \kappa (b_2+\bar{b}_2^*(\epsilon))^{\frac{1}{2}} \cdot \epsilon}$ as $\epsilon$ goes to 0?)
	Then, for any $\epsilon_1>0$, we can choose $\bar{b}_2$ large enough, say $\bar{b}_2 \geq \bar{b}_2^{**} > \bar{b}_2^*$, so that
	\begin{equation}
	(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2,t_2) }   \leq \epsilon_1.
	\label{eq:limit_p_f(p)}
	\end{equation}

>>>>

	Our next step is to show that $(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2,t_2) } $ tends towards $0$ when $\bar{b}_2 \to \infty$. We showed above that for all $t \in [0,T]$, $f(\bar{b}_2,t) \to c_3 >0$. Let $c_{b_2}$ such that $0<c_{b_2} <\frac{c_3}{2} $. Then there exists $\bar{b}_2^* := \bar{b}_2^*(c_{b_2},t_2)>0$ so that for all $\bar{b}_2 \geq \bar{b}_2^*$ we have $\vert f(\bar{b}_2,t_2) - c_3 \vert < c_{b_2}$. Then $f(\bar{b}_2,t_2) - c_3 + 2c_{b_2} > c_{b_2}$ and 
	\begin{equation*}
	\begin{array}{rl}
		(b_2 + \bar{b}_2) e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} f(\bar{b}_2,t_2) }  &= e^{- \kappa (b_2 + \bar{b}_2)^{\frac{1}{2}} (f(\bar{b}_2,t_2) - c_3 + 2c_{b_2}) }\cdot e^{- \kappa  (c_3 - 2 c_{b_2}) (b_2 + \bar{b}_2)^{\frac{1}{2}} +  \ln (b_2 + \bar{b}_2) } \\
		& \leq  e^{- \kappa (b_2+\bar{b}_2^*)^{\frac{1}{2}} \cdot c_{b_2}} \cdot e^{- \kappa (c_3 - 2 c_{b_2}) (b_2 + \bar{b}_2)^{\frac{1}{2}} + \ln (b_2 + \bar{b}_2)} \\
		&=:c_5 e^{- \kappa (c_3 - 2 c_{b_2}) (b_2 + \bar{b}_2)^{\frac{1}{2}} + \ln (b_2 + \bar{b}_2)} \\
		& \xrightarrow[\bar{b}_2 \to \infty]{}0.
	\end{array}
	\end{equation*}
